### 2016-03-10 manuscript.Rnw
[fix #11] add link to definition of properties
change wording slightly

Criteria that can be used to search for studies or their associated trees are
available through the output of the function
\texttt{studies\_properties}. Typically, users will want to search for studies
or trees based on taxon names (or their OTT identifiers), but other
criteria such as the title of the publication can be used. Here we demonstrate
how to look for and retrieve trees for studies focusing on the family Felidae
(Figure~\ref{fig:plot_cats}).

@@

Here we show how we can obtain a map of the occurrences for a subset of the cat
species (genus \textit{Lynx}) that were included in the phylogeny retrieved from
the Felidae study above. We extract the species names from the phylogeny, and use
them to ask for the records for these species found in GBIF
(Figure~\ref{fig:cat_map}). We include the code to reproduce this figure in the
Appendix.

>>>>

Criteria that can be used to search for studies or their associated trees are
available through the output of the function
\texttt{studies\_properties}. The meaning of these properties is described at:
\url{https://github.com/OpenTreeOfLife/phylesystem-api/wiki/NexSON}. Typically,
users will want to search for studies or trees based on taxon names (or their
OTT identifiers), but other criteria such as the title of the publication can be
used. Here we demonstrate how to look for and retrieve trees for studies
focusing on the family Felidae (Figure~\ref{fig:plot_cats}).

@@

Here we show how we can obtain a map of the occurrences for a subset of the cat
species that were included in the phylogeny retrieved from the Felidae study
above (genus \textit{Lynx}). We extract the species names from the phylogeny,
and use them to ask for the records for these species found in GBIF
(Figure~\ref{fig:cat_map}). We include the code to reproduce this figure in
Appendix.
